---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# yang7er

<!-- badges: start -->

<!-- badges: end -->

The goal of yang7er is to calculating the difference between state and regional hpi, as well as graphing the change in state hpi, and the change in regional hpi.

## Installation

You can install the development version of yang7er from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("etc5523-2022/rpkg-yang7er")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(yang7er)
## basic example code
```

### 1.get_hpi

If you want to check the build-in data, you can use:

```{r}
get_hpi()
```

### 2.diff_region_state

If you want to get the information of `Ak`, in `2006`, you can use:

```{r}
diff_region_state("AK",2016)
```

### 3.diff_plot

If you want to plot the `AK's` hpi change, and compare with its region's change, you can use:

```{r plot1, fig.cap="The change of HPI in Ak, Pacific West Area",fig.width=5.5,fig.height=4}
diff_plot("AK")
```

### 4.regions_plot

If you want to plot regions' hpi change from `1990` to `2018`, you can use:

```{r plot2, fig.cap="The change of HPI in all regions from 1990 to 2018",fig.width=5.5,fig.height=4}
regions_plot(1990,2018)
```
