---
title: "Guide to yang7er"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Guide to yang7er}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r,include = FALSE}
library(tidyverse)
library(kableExtra)
```

# Description

yang7er provides the calculation of the difference between state and regional hpi, as well as graphing the change in state hpi, and the change in regional hpi.

A house price index (HPI) measures the price changes of residential housing as a percentage change from some specific start date (which has an HPI of 100). The built-in data in this package comes from Federal Housing Finance Agency, it included the HPI in US by states from 1975 to 2018.

This vignette shows you how to derive the HPI difference between a state and its region, an image of the state's HPI change, and an image of the region's change using the yang7er package

Load the yang7er package using the library() function.

```{r setup}
library(yang7er)
```

## Built-in data description

```{r,echo=FALSE}
Description <- c("year","month","states in US","house price index","us annual average HPI","every stats's anaual average HPI","us annual average HPI","state belongs in which region","every region's anaual average HPI")
codebook <- tibble(Variable = colnames(hpi),
       Type = map_chr(hpi, typeof)) %>%
  mutate(Description = Description)

kable(codebook, align = "lc",
      caption = "HPI Data Description") %>%
  kable_styling(full_width = F, 
                bootstrap_options = c("striped", "condensed", "bordered"))
```

The HPI data sets needed for this blog comes from the Federal Housing Finance Agency, which is a tabular data with `26877` rows and `9` columns of data. More details about this dataset can be found by using the function `help(hpi)`

## Example of the Package

### 1.get_hpi

If you want to check the build-in data, you can use:

```{r}
get_hpi()
```

### 2.diff_region_state

If you want to get the information of `Ak`, in `2006`, you can use:

```{r}
diff_region_state("AK",2016)
```

### 3.diff_plot

If you want to plot the `AK's` hpi change, and compare with its region's change, you can use:

```{r plot1, fig.cap="The change of HPI in Ak, Pacific West Area",fig.width=5.5,fig.height=4}
diff_plot("AK")
```

### 4.regions_plot

If you want to plot regions' hpi change from `1990` to `2018`, you can use:

```{r plot2, fig.cap="The change of HPI in all regions from 1990 to 2018",fig.width=5.5,fig.height=4}
regions_plot(1990,2018)
```
